\documentclass[wes, manuscript]{copernicus}

\begin{document}

\title{Coupled Wind Turbine Layout and Design Optimization with Non-Homogeneous Wind Turbines}

\Author[1]{Andrew P.J.}{Stanley}
\Author[1]{Andrew}{Ning}

\affil[1]{Department of Mechanical Engineering, Brigham Young University, Provo, UT, 84602, USA}

\runningtitle{TEXT}

\runningauthor{TEXT}

\correspondence{Andrew PJ Stanley (stanley\_andrewpj@byu.net)}



\received{}
\pubdiscuss{} 
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.


\firstpage{1}

\maketitle



\begin{abstract}
In this study, wind farms are optimized to show the benefit of coupling turbine design and layout optimization, as well as including different turbine designs in a single wind farm. For our purposes, turbine design includes hub height, rotor diameter, rated power, tower diameter, tower shell thickness, and implicit blade chord and twist distributions. A 32-turbine wind farm and a 60-turbine wind farm are both considered, as well as a variety of turbine spacings and wind shear exponents. Structural constraints as well as turbine costs are considered in the optimization. Results indicate that coupled turbine design and layout optimization is superior to sequentially optimizing turbine design, then turbine layout. Coupled optimization results in an additional  2--5\% reduction in cost of energy compared to optimizing sequentially. Furthermore, wind farms with closely spaced wind turbines can greatly benefit from non-uniform turbine design throughout the farm. Some of these wind farms with heterogeneous turbine design have an additional 10\% cost of energy reduction compared to wind farms with identical turbines throughout the farm.
\end{abstract}


%\copyrightstatement{TEXT}


\introduction 
\input{Sections/Introduction}




\section{Methodology}

	\subsection{Wake Model}
	\input{Sections/wake_model}
      
	\subsection{Annual Energy Production Calculation}
	\input{Sections/AEP_calc}

	\subsection{Tower Model}
	\input{Sections/tower_model}

	\subsection{Rotor/Nacelle Models}
	\input{Sections/rotor-nacelle_models}

	\subsection{Cost Model}
	\input{Sections/cost_model}

	\subsection{Optimization}
	\label{sec:optimization}
	\input{Sections/optimization}




\section{Results}
\input{Sections/new_results}


\conclusions 
\input{Sections/conclusions}


%% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
%% It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.


\codedataavailability{Forthcoming} %% use this section when having data sets and software code available


\competinginterests{The authors declare that they have no conflict of interest.} %% this section is mandatory even if you declare that no competing interests are present

\begin{acknowledgements}
The authors developed this journal article based on funding from the Alliance for Sustainable Energy, LLC, Managing and Operating Contractor for the National Renewable Energy Laboratory for the U.S. Department of Energy. 

Funding for the work was provided by the DOE Office of Energy Efficiency and Renewable Energy, Wind Energy Technologies Office.

The U.S. Government retains and the publisher, by accepting the article for publication, acknowledges that the U.S. Government retains a nonexclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this work, or allow others to do so, for U.S. Government purposes.
\end{acknowledgements}



%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
\bibliographystyle{copernicus}
\bibliography{references.bib}

\end{document}
